---
title: "Problem Set 5"
author: "Corey McCrea and Will Crewe"
subtitle: MGSC 310 Problem Set 5
output:
  html_document:
    df_print: paged
  html_notebook: default
---

```{r setup, include=FALSE}
library(knitr)
# As long as you are working in a Rstudio Project file, you shouldn't need to 'hard code' directories like this 
# change to your own working directory
# knitr::opts_knit$set(root.dir = 'C:/Users/hersh/Dropbox/Chapman/Teaching/MGSC_310/Fall_2019/problem_sets')
# setwd('C:/Users/hersh/Dropbox/Chapman/Teaching/MGSC_310/Fall_2019/problem_sets')

# set seed to your own favorite number
set.seed(1818)
options(width=70)
options(scipen=99)


# general rchunk code options

# this sets text to small
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=TRUE, size = "vsmall")  
opts_chunk$set(message = FALSE,                                          
               warning = FALSE,
               # "caching" stores objects in code chunks and only rewrites if you change things
               cache = TRUE,                               
               # automatically downloads dependency files
               autodep = TRUE,
               # 
               cache.comments = FALSE,
               # 
               collapse = TRUE,
               fig.width = 5,  
               fig.height = 4,
               fig.align='center')


```

## Question 1

1a) See below

```{r}
library("tidyverse")
options(scipen = 50)
set.seed(1861)
movies <- read.csv(here::here("datasets", "IMDB_movies.csv"))
movies <- movies %>% filter(budget < 4e+08) %>% filter(content_rating != 
    "", content_rating != "Not Rated", plot_keywords != "", !is.na(gross))
movies <- movies %>% mutate(genre_main = unlist(map(strsplit(as.character(movies$genres), 
    "\\|"), 1)), plot_main = unlist(map(strsplit(as.character(movies$plot_keywords), 
    "\\|"), 1)), grossM = gross/1e+06, budgetM = budget/1e+06)
movies <- movies %>% mutate(genre_main = fct_lump(genre_main, 
    7), plot_first = fct_lump(plot_main, 20), content_rating = fct_lump(content_rating, 
    4), country = fct_lump(country, 8), language = fct_lump(language, 
    4), cast_total_facebook_likes000s = cast_total_facebook_likes/1000) %>% 
    drop_na()

top_director <- movies %>% group_by(director_name) %>% summarize(num_films = n()) %>% 
    top_frac(0.1) %>% mutate(top_director = 1) %>% select(-num_films)

movies <- movies %>% left_join(top_director, by = "director_name") %>% 
    mutate(top_director = replace_na(top_director, 0)) %>% select(-c(director_name, 
    actor_2_name, gross, genres, actor_1_name, movie_title, actor_3_name, 
    plot_keywords, movie_imdb_link, budget, color, aspect_ratio, 
    plot_main, actor_3_facebook_likes, actor_2_facebook_likes, 
    color, num_critic_for_reviews, num_voted_users, num_user_for_reviews, 
    actor_2_facebook_likes))

sapply(movies %>% select_if(is.factor), table)
## $language
## 
##  English   French Mandarin  Spanish    Other 
##     3576       32       13       22       70 
## 
## $country
## 
## Australia    Canada     China    France   Germany Hong Kong 
##        39        57        13        97        79        13 
##     Spain        UK       USA     Other 
##        19       315      2974       107 
## 
## $content_rating
## 
##     G    PG PG-13     R Other 
##    87   565  1306  1694    61 
## 
## $genre_main
## 
##    Action Adventure Biography    Comedy     Crime     Drama 
##       952       367       204       979       250       654 
##    Horror     Other 
##       163       144 
## 
## $plot_first
## 
##            1950s            1970s            actor 
##               18               18               24 
## african american            alien        apartment 
##               24               69               19 
##             army         assassin             baby 
##               20               26               22 
##             bank              bar       basketball 
##               19               18               18 
##           battle            beach      best friend 
##               26               19               32 
##  box office flop              boy        christmas 
##               28               36               18 
##              cia          college            death 
##               19               22               40 
##           friend            Other 
##               21             3157

library("rsample")

movies_split <- initial_split(movies, p = 0.75)

movies_train <- training(movies_split)
movies_test <- testing(movies_split)
```


1b) The plot keywords that are associated with the most blockbusters are: battle, college, friend.

```{r}
library("ggridges")
ggplot(movies, aes(grossM, plot_first)) + geom_density_ridges()
```

1c) 
```{r}
library(partykit)
library(tidyverse)
library(titanic)
library(PerformanceAnalytics)
library(rpart)       
library(rpart.plot)  
library('randomForest')
cust_boot_preds <- movies_train %>% rownames_to_column() %>% 
  mutate(rowname = as.numeric(rowname))
B <- 100
num_b <- 500
boot_mods <- list() 
for(i in 1:B){
  boot_idx <- sample(1:nrow(movies_train), 
                     size = num_b,
                     replace = FALSE)
  boot_tree <- ctree(grossM ~ ., 
                     data = movies_train %>% 
                       slice(boot_idx)) 
  boot_mods[[i]] <- boot_tree
  preds_boot <- data.frame(
    preds_boot = predict(boot_tree),
    rowname = boot_idx 
  )  
  names(preds_boot)[1] <- paste("preds_boot",i,sep = "")
  cust_boot_preds <- left_join(x = cust_boot_preds, y = preds_boot,
                                  by = "rowname")
}

```


1d)
```{r}
#preds_bag <- cust_boot_preds %>% summarise(c_across(preds_boot1:preds_boot100))

cust_boot_preds <- cust_boot_preds %>% 
  mutate(preds_bag = 
           select(., preds_boot1:preds_boot100) %>% 
           rowMeans(na.rm = TRUE))

```


1e) 
```{r}
library('yardstick')
rmse(cust_boot_preds, grossM, preds_bag)
rsq(cust_boot_preds, grossM, preds_bag)
mae(cust_boot_preds, grossM, preds_bag)
```



1f)
```{r}
rf_fit <- randomForest(grossM ~ ., 
                       data = movies_train,
                       mtry = sqrt(17),
                       na.action = na.roughfix,
                       ntree = 200)
```



1g) There are 17 columns in the dataset so we use the square root of 17

1h) The error drastically reduces as we increase the number of trees from 1 to 50 and continues to go down as we approach
200 but much less drastically.
```{r}
plot(rf_fit)
```

1i) The top 5 most important variables are budgetM, movie_facebook_likes, imdb_score, duration, genre_main.
```{r}
varImpPlot(rf_fit)
```



1l) We couldn't get this last error figured out about probability or vote not meaningful for regression
```{r}

preds_train_res <- predict(rf_fit, movies_train, type = "response")
preds_test_res <- predict(rf_fit, movies_test, type = "response")
#preds_train_prob <- predict(rf_fit, movies_train, type = "prob")
#preds_test_prob <- predict(rf_fit, movies_test, type = "prob")
#preds_train_votes <- predict(rf_fit, movies_train, type = "vote")
#preds_test_votes <- predict(rf_fit, movies_test, type = "vote")

#results_test <- data.frame(
#  `RMSE` = c(rmse(movies_test, preds_test_res, grossM),
#             rmse(movies_test, preds_test_prob, grossM),
#             rmse(movies_test, preds_test_votes, grossM)),
#  `RSQ` =  c(rsq(movies_test, preds_test_res, grossM),
#             rsq(movies_test, preds_test_prob, grossM),
#             rsq(movies_test, preds_test_votes, grossM)),
#  `MAE` =  c(mae(movies_test, preds_test_res, grossM),
#             mae(movies_test, preds_test_prob, grossM),
#             mae(movies_test, preds_test_votes, grossM)),
#  `Type` = c("response","prob","votes"))




```












































