---
title: "Problem Set 1"
author: "Corey McCrea"
subtitle: MGSC 310, Fall 2020, Zoom Professor Hersh
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
library(ggplot2)
library(magrittr)
library(formatR)
knitr::opts_chunk$set(echo = TRUE)

# set seed to your own favorite number
set.seed(542)
options(width=70)
options(scipen=99)


# general rchunk code options

# this sets text to small
opts_chunk$set(tidy.opts=list(width.wrap=50),tidy=TRUE, size = "vsmall")  
opts_chunk$set(message = FALSE,                                          
               warning = FALSE,
               # "caching" stores objects in code chunks and only rewrites if you change things
               cache = TRUE,                               
               # automatically downloads dependency files
               autodep = TRUE,
               # 
               cache.comments = FALSE,
               # 
               collapse = TRUE,
               fig.width = 5,  
               fig.height = 4,
               fig.align='center')
```

## Question 2

a) **dir_ls()** Returns the files and folders in the current working directory.

```{r}
library(fs)
dir_ls()
```
b) Reading CSV
```{r}
movies <- read.csv(here::here("datasets", "IMDB_Movies.csv"))
```

c) 5043 Rows and 28 Columns
```{r}
dim(movies)
```
d) See below
```{r}
names(movies)
```
e) The following are character strings
* color
* director_name
* genres
* actor_1_name
* movie_title
* plot_keywords
* movie_imdb_link
* language
* country
* content_rating

```{r}
movies %>% glimpse()
```
f) See below
```{r}
movies %>% slice(1:5)
```
g) James Cameron
```{r}
movies %>% arrange(-gross) %>% slice(1:10)

```

h) 

```{r}
movies_sub <- movies %>% select(-movie_imdb_link)
dim(movies_sub)
```
g) The pipe operator can be used to feed outputs into other inputs. It makes things a bit easier to read and understand, especially when there is a lot going on with a certain function.The only downside is it is a pain to type. The pipe operated could be used like **myData %>% head()** instead of **head(myData)** for example. The **arrange()** function can be used to sort your data based on a column of your choosing. If you want to reverse the sorting you can include a *-* for example **myData %>% arrange(-someColumn)**. The **select()** function is used to take a subset of your data if you want to look at certain columns. You can also include a *-* to include everything except a certain column. **glimpse() ** is very useful for getting a preview of your data. It prints all the columns and some sample entries along with the type of data the column is set to. Finally **slice()** can be used to look at certain rows i.e. **myData %>% slice(10:20)** if you wanted to look at certain rows in a dataset.

##Question 3

a)

```{r}

ggplot(movies ,aes(imdb_score, gross)) + geom_point()

```
b)
```{r}
ggplot(movies ,aes(imdb_score, gross)) + geom_point(alpha = 1/10)

```
c)
```{r}

movies %<>% mutate(gross_M = gross/1000000)

```

d)  Yes there is a positive correlation between gross and IMDB score

```{r}

ggplot(movies, aes(imdb_score, gross_M)) + geom_smooth(model = lm)

```

e)
```{r}
ggplot(movies%>% filter(director_name == "James Cameron"), aes(imdb_score, gross_M)) + geom_text(aes(label = movie_title), color = "magenta")

```

f)
```{r}
ggplot(movies%>% filter(director_name == "James Cameron"), aes(imdb_score, gross_M)) + geom_text(aes(label = movie_title), color = "magenta") + xlim(7,9) + ylim(0,800)
```
g)
```{r}
ggplot(movies%>% filter(director_name == "James Cameron"), aes(imdb_score, gross_M)) + 
  geom_text(aes(label = movie_title), color = "magenta") + 
  xlim(7,9) + ylim(0,800) + 
  xlab("IMDB Score") + ylab("Gross in Millions") +
  ggtitle(label = "Movie Gross vs. IMDB Score of James Cameron Movies")

```
h)

```{r}
p <- ggplot(movies%>% filter(director_name == "James Cameron"), aes(imdb_score, gross_M)) + 
    geom_text(aes(label = movie_title), color = "magenta") + 
    xlim(7,9) + ylim(0,800) + 
    xlab("IMDB Score") + ylab("Gross in Millions") +
    ggtitle(label = "Movie Gross vs. IMDB Score of James Cameron Movies")

ggsave("MoviePlot.jpg", p, width = 6, height = 4)

```










